# Centrality

## Bird 7358 {.panelset}

### Distance from centroid

Euclidean distance for each syllable to the centroid of it's cluster in embedded space.

```{r centrality-7358-distance, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Distance from centroid - Bird 7358', full.names = T)
knitr::include_graphics(filenames)
```

### Centrality

Centrality $C$ is the sum of the inverse Euclidean distances $d$ of the embedded dimensions $u$.

\begin{equation}
\LARGE
  \begin{array}{l}
    C_i =\sum\limits_{j=1}^n \frac{1}{d(u_i,u_j)} \\
    (\#eq:Centrality)
  \end{array}
\end{equation}

```{r centrality-7358-Centrality, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Centrality - Bird 7358', full.names = T)
knitr::include_graphics(filenames)
```

### Clustering Coefficient

\begin{equation}
\LARGE
  \begin{array}{l}
    K_i =\sum\limits_j w_{ij} \\
    C_i=\frac{\sum_{k,j} (w_{ik}w_{ij}w_{kj})^\frac{1}{3}}{K_i(K_i-1)} = \frac{\mathrm{diag}((w^\frac{1}{3})^3)}{K_i(K_i-1)}
    (\#eq:Clustering)
  \end{array}
\end{equation}

```{r centrality-7358-Clustering-Coefficient, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Clustering Coefficient - Bird 7358', full.names = T)
knitr::include_graphics(filenames)
```

### Pagerank
```{r centrality-7358-Pagerank, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Pagerank - Bird 7358', full.names = T)
knitr::include_graphics(filenames)
```



## Bird 6951 {.panelset}
### Distance from centroid
```{r centrality-6951-distance, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Distance from centroid - Bird 6951', full.names = T)
knitr::include_graphics(filenames)
```

### Centrality
```{r centrality-6951-Centrality, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Centrality - Bird 6951', full.names = T)
knitr::include_graphics(filenames)
```

### Clustering Coefficient
```{r centrality-6951-Clustering-Coefficient, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Clustering Coefficient - Bird 6951', full.names = T)
knitr::include_graphics(filenames)
```

### Pagerank
```{r centrality-6951-Pagerank, out.width='100%'}
filenames = list.files(path = 'Figures/Syllable distance/', 
                    pattern = 'violin - Pagerank - Bird 6951', full.names = T)
knitr::include_graphics(filenames)
```


